---
title: "SRRun2strain_output"
author: "snakemake"
date: "`r Sys.Date()`"
params:
  instrain_dir: instrain_santosviromes
  lifestyle_file: santosviromes_phatyp_prediction.tsv
  working_dir: /Users/thomasdebruijn/Documents/PhD/R_PhD
  data_dir: /Users/thomasdebruijn/Documents/PhD/DATASETS
  bioproject_id: PRJNA646773
  install: False
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    source_code: embed
    favicon: "table-solid.svg"
---

```{r setup, include=FALSE, echo=F}
knitr::opts_chunk$set(echo = TRUE)

# Run script
master_script.file <- "SRRrun2strain_data_combination.R"
master_script.data <- readLines(master_script.file)

print(params$instrain_dir)

# Overload commandArgs function with our params
commandArgs_custom <- list(
    instrain_dir = params$instrain_dir,
    lifestyle_file = params$lifestyle_file,
    wd = params$working_dir,
    data_wd = params$data_dir,
    install = params$install,
    bioproject_id = params$bioproject_id
)

# Run our r master script with our parameters (implicit)
source(master_script.file, local = knitr::knit_global())
```

# General info

```{r info function block, include=F}
# Declare functions
computeSamplesTotal = function(temp.data.stat){
  return(length(unique(temp.data.stat$SRR_ID)))
}
computevOTUsTotal = function(temp.clean.data){
  return(length(unique(temp.clean.data$genome_ID)))
} 


```

## Row 1

### Samples (SRR_IDs) in dataset

```{r, echo=F}
total.samples = computeSamplesTotal(main.clean.stat.data)
valueBox(total.samples, icon = "fa-solid fa-dna")
```

### vOTUs in dataset

```{r, echo=F}
total.vOTUs = computevOTUsTotal(main.clean.data)
valueBox(total.vOTUs, icon = "fa-solid fa-chart-line")
```

### Samples in dataset

```{r, echo=F}
valueBox(value = commandArgs_custom$bioproject_id, icon = "fa-solid fa-hashtag", 
         caption = commandArgs_custom$instrain_dir)
```

## Row 2 {data-height="600"}

### Table containing quick statistics {data-width="250"}

```{r Summary statistics whole dataset by lifestyle, echo=F}
rmarkdown::paged_table(main.data.summary.stats, options = list(rows.print = 30,
                                                               cols.print = 15,
                                                               max.print = 300))
```

### Aditional file info {data-width="300" max-width="300"}

Data was generated using the SRRun2strain snakemake pipeline. More information on output files can be found under the **meta-data** tab. Visualisations based on main output files are contained within this report, as well as some example data in tabular format.

For more information on the workings of the pipeline, go to the [git repo](https://git.wur.nl/thomas.debruijn/srr2instrain). The various scripts used in this pipeline are also explained there.

This is the **general info** tab, containing an overview of the dataset.

# Tabular data

### Statistics on per sample basis

```{r table clean statistics data, echo=F}
rmarkdown::paged_table(main.clean.stat.data, options = list(rows.print = 30,
                                                               cols.print = 15,
                                                               max.print = 300))
```

# Plot data

## Row 1 {.tabset .tabset-fade data-height="2000"}

### Total samples microdiversity plot

```{r SRR ID microdiversity plot, echo=F, fig.dpi=400, fig.height=20, fig.width=8, fig.align='center'}
p.interval.microdiversity_bysample
```

### Mapping stats by SRR_ID plot

#### 

##### 

```{r SRR ID breadth plot, echo=F, fig.height=6.5}
ggplotly(p.bar.breadth_bysample)
```

##### 

```{r SRR ID coverage plot, echo=F, fig.height=6.5}
ggplotly(p.bar.coverage_bysample)
```

##### 

```{r SRR ID length plot, echo=F, fig.height=6.5}
ggplotly(p.bar.length_bysample)
```

# Meta-data

Scripts and related information used to analyze data used in this report. Source code for the rmarkdown file can be found in the upper right corner.

## Row 1 {.tabset data-height="1000"}

### R master script

```{r source-code master script, echo=F, attr.output='style="max-height: 100%;"'}
cat(master_script.data, sep = "\n")
```
